\bf Reinforcement learning

### 2018-03-25 presentations/presentation_rl/presentation.tex
rl presentation

\begin{frame}{\bf Problem definition}
\begin{itemize}
 \item learn to play game with unknow rules
 \item input  : state and reward
 \item output : action and total score
\end{itemize}
\centering

{\bf Agent never see required value (required action)}

@@

\begin{frame}{\bf Neural network example - deep reinforcement learning}

@@

>>>>

\begin{frame}{\bf Problem definition}
\begin{itemize}
 \item learn to play game with unknow rules
 \item input  : state and reward
 \item output : action and total score
 \item $Q(s, a)$ : learn Q function
\end{itemize}
\centering

{\color{red} \bf agent never sees required value (required action)}

@@

\begin{frame}{\bf Neural network approximator - deep reinforcement learning}

@@

\begin{frame}{\bf Speed up learning}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.21]{../../diagrams/fnn.png}
  \caption*{common feed forward neural network}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.21]{../../diagrams/hnn.png}
  \caption*{stacked autoencoder + feed forward neural network}
\end{figure}

\begin{frame}{\bf Sparse weights}

\begin{equation*}
  \label{eq:weights_training}
  \Delta w = \eta E x \frac{df(y)}{dw} - \lambda sgn(w)
\end{equation*}

where \\
$E$ is error, \\
$x$ is input, \\
$y$ is output, \\
$f$ is activation function (ReLU, tanh, softmax ...), \\
$\eta$ is learning rate , \\
$\lambda$ is sparsity parameter

\begin{frame}{\bf Arcade game experiment}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.21]{../../diagrams/arcade_rl_game_desc.png}
\end{figure}

{
\tiny

\begin{table}[!h]
\centering
\begin{tabular}{|l|l|l|l|l|}
\hline
                        & FNN sparse & FNN no sparse & AE+FNN  sparse & AE+FNN no sparse \\ \hline
unsupervised iterations & 0          & 0             & 100000         & 100000           \\ \hline
supervised iterations   & 200000     & 200000        & 200000         & 200000           \\ \hline
iterations per slice    & 0          & 0             & 50000          & 50000            \\ \hline
learning rate           & 0.0005     & 0.0005        & 0.0005         & 0.0005           \\ \hline
init weight range       & 0.1        & 0.1           & 0.1            & 0.1              \\ \hline
dropout                 & 0          & 0             & 0              & 0                \\ \hline
lambda                  & 0.00000001 & 0             & 0.00000001     & 0                \\ \hline
\end{tabular}
\end{table}

}

\begin{frame}{\bf Sparsity results}

\begin{figure}[!htb]
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[scale=0.15]{../../results/rl_arcade/fnn_trained_0/supervised/layer_1_histogram.png}
  \captionof*{figure}{\tiny FNN sparse weights histogram}
  \label{img:FNN sparse weights histogram}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[scale=0.15]{../../results/rl_arcade/fnn_trained_5/supervised/layer_1_histogram.png}
  \captionof*{figure}{\tiny FNN no sparse weights histogram}
  \label{img:FNN no sparse weights histogram}
\end{minipage}
\end{figure}

\begin{figure}[!htb]
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[scale=0.15]{../../results/rl_arcade/hnn_trained_0/supervised/layer_1_histogram.png}
  \captionof*{figure}{\tiny AE+FNN sparse weights histogram}
  \label{img:AE+FNN sparse weights histogram}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[scale=0.15]{../../results/rl_arcade/hnn_trained_5/supervised/layer_1_histogram.png}
  \captionof*{figure}{\tiny AE+FNN no sparse weights histogram}
  \label{img:AE+FNN no sparse weights histogram}
\end{minipage}
\end{figure}

\begin{frame}{\bf Sparsity results}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.4]{../../diagrams/layer_1_fnn_sparse.png}
  \caption*{FNN sparse weights visualisation}
  \label{img:FNN sparse weights visualisation}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.4]{../../diagrams/layer_1_hnn_sparse.png}
  \caption*{AE+FNN sparse weights visualisation}
  \label{img:AE+FNN sparse weights visualisation}
\end{figure}

\begin{frame}{\bf Score results}

\begin{figure}[!htb]
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[scale=0.15]{../../results/rl_arcade/fnn_progress/training_progress.png}
  \captionof*{figure}{\tiny FNN progress comparison}
  \label{img:FNN progress comparison}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[scale=0.15]{../../results/rl_arcade/hnn_progress/training_progress.png}
  \captionof*{figure}{\tiny AE+FNN progress comparison}
  \label{img:AE+FNN progress comparison}
\end{minipage}
\end{figure}

\begin{figure}[!htb]
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[scale=0.15]{../../results/rl_arcade/fnn_progress/testing_score.png}
  \captionof*{figure}{\tiny FNN score}
  \label{img:FNN score}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[scale=0.15]{../../results/rl_arcade/hnn_progress/testing_score.png}
  \captionof*{figure}{\tiny AE+FNN score}
  \label{img:AE+FNN score}
\end{minipage}
\end{figure}

\begin{frame}{\bf Results}

\begin{figure}[!h]
  \centering
  \includegraphics[scale=0.25]{../../results/rl_arcade/training_progress.png}
  \caption*{Training progress comparison}
  \label{img:Training progress comparison}
\end{figure}

{
\tiny
\begin{table}[]
\centering
\label{tab:summary_results}
\begin{tabular}{|l|c|c|c|c|}
\hline
                         & \multicolumn{1}{l|}{average score} & \multicolumn{1}{l|}{best score} & \multicolumn{1}{l|}{worst score} & \multicolumn{1}{l|}{average best action probability {[}\%{]}} \\ \hline
FNN sparse weights       & 960.58                             & 994.97                          & 922.64                           & 95.32                                                         \\ \hline
FNN nosparse weights     & 945.04                             & 995.64                          & 878.31                           & 93.29                                                         \\ \hline
AE+FNN sparse weights    & 914.5                              & 947.64                          & 875.31                           & 93.4                                                          \\ \hline
AE+FNN no sparse weights & 908.58                             & 954.31                          & 780.32                           & 93.12                                                         \\ \hline
\end{tabular}
\end{table}
}

\begin{frame}{\bf Snake game experiment}

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.15]{../../diagrams/worms_rl_game_desc.png}
\end{figure}

\begin{figure}[!htb]
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[scale=0.17]{../../results/rl_worms/fnn_progress/training_progress.png}
  \captionof*{figure}{FNN score progress comparison}
  \label{img:worms FNN score progress comparison}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[scale=0.17]{../../results/rl_worms/hnn_progress/training_progress.png}
  \captionof*{figure}{AE+FNN score progress comparison}
  \label{img:worms AE+FNN score progress comparison}
\end{minipage}
\end{figure}

\begin{frame}{\bf Snake game experiment}

\begin{figure}[!h]
  \centering
  \includegraphics[scale=0.3]{../../results/rl_worms/training_progress.png}
  \caption*{Training worms score progress for best networks}
  \label{img:Training worms score progress for best networks}
\end{figure}
